\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
delete repetitive reference to appendix
delete stray parenthesis

Here we report about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes. We detail what each participant did in Appendix~\ref{summary}.

@@

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges}) summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

>>>>

Here we report about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes.

@@

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.
